% !TEX root = epifanov_solid_state_physics.tex
%!TEX TS-program = pdflatex
%!TEX encoding = UTF-8 Unicode


\chapter*{Bibliography}
\addcontentsline{toc}{chapter}{Bibliography}
\chaptermark{Bibliography}

\parindent=0mm

\vspace*{-12pt}

{\large{\sffamily\bfseries General}}

{\small

\textbf{0.1.} V. L. Bonch-Bruevich and S. G. Kalashnikov: Semiconductor Physics, ``Nauka'', Moscow (1977) (in Russian).

\textbf{0.2.} G. I. Epifanov: Physical Principles of Microelectronics, Mir Publishers, Moscow (1974).

\textbf{0.3.} P. T. Oreshkin: Physics of Semiconductors and Dielectrics, ``Vysshaya Shkola'', Moscow (1977) (in Russian).

\textbf{0.4.} L. S. Stil'bans: Semiconductor Physics, ``Sovetskoe radio'', Moscow (1967) (in Russian).

\textbf{0.5.} K. V. Shalimova: Semiconductor Physics, ``Energiya'', Moscow (1976)
(in Russian).

\textbf{0.6.} V. V. Novikov: Theoretical Foundation of Microelectronics, ``Vysshaya shkola'', Moscow (1972) (in Russian).

\textbf{0.7.} J. M. Ziman: Principles of the Theory of Solids (2nd edition), Cambridge U.P., London (1970).

\textbf{0.8.} R. L. Sproull: Modern Physics (2nd edition), Wiley, New York (1964).

\textbf{0.9.} K. Seeger: Semiconductor Physics, Springer, Wien (1973).

}

\bigskip

{\large{\sffamily\bfseries Chapter 1}}

\small{

\textbf{1.1.} G. C. Pimentel and R. D. Spratley: Chemical Bonding Clarified Through Quantum Mechanics, Holden-Day, San Francisco (1969).

\textbf{1.2.} W. Haberditzl: Bausteine der Materie und chemische Binding, Deutscher Verlag der Wissenschaften, Berlin (1972).

\textbf{1.3.} L. Pauling: General Chemistry (3rd edition), W. H. Freeman, San Francisco (1970).

\textbf{1.4.} J. A. Campbell: Chemical Systems, W. H. Freeman, San Francisco (1970).

\textbf{1.5.} J. Ficini, N. Lumbroso-Bader, and J.-C. Depezay: Elements de chimiephysique, Hermann, Paris (1968-69).

\textbf{1.6.} C. A. Wert and R. M. Thomson: Physics of Solids (2nd edition), McGraw-Hill, New York (1970).

}

\bigskip

{\large{\sffamily\bfseries Chapter 2}}

{\small

\textbf{2.1.} Ya. I. Frenkel: Introduction to the Theory of Metals (4th edition), ``Nauka'', Moscow (1972) (in Russian).

\textbf{2.2.} M. Kh. Rabinovich: Strength and Superstrength of Metals, Izd-vo Akad. Nauk SSSR, Moscow (1963) (in Russian); Strength, Temperature, Time, ``Nauka'', Moscow (1968) (in Russian).

\textbf{2.3.} A. V. Stepanov: Fundamentals of the Theory of Practical Strength of Crystals, ``Nauka'', Moscow (1974) (in Russian).

\textbf{2.4.} G. M. Bartenev and Yu. S. Zuev: Strength and Rupture of Hyperelastic Materials, ``Khimiya'', Moscow-Leningrad (1964) (in Russian).

\textbf{2.5.} Physical Metallurgy, R. W. Cahn (Ed.), North-Holland, Amsterdam (1965).

\textbf{2.6.} Fracture, H. Liebowits (Ed.), Academic Press, New York (1972).

\textbf{2.7.} F. A. McCerntrock and A. S. Argon: Mechanical Behaviour of Materials, Addison-Wesley, Reading, Mass. (1966).

\textbf{2.8.} See 1.6.

}

\bigskip

{\large{\sffamily\bfseries Chapter 3}}

{\small

\textbf{3.1.} V. G. Levich: Introduction to Statistical Physics (2nd edition), GITTL, Moscow (1954) (in Russian).

\textbf{3.2.} F. Reif: Statistical Physics (Berkeley Physics Course, Vol. 5), McGraw-Hill, New York (1972).

\textbf{3.3.} H. Bethe and A. Sommerfeld: Electronentheorie der Metalle, Springer, Berlin (1933).

\textbf{3.4.} C. Kittel: Introduction to Solid State Physics (4th edition), Wiley, New York (1971); Elementary Solid State Physics: A Short Course, Wiley, New York (1962).

\textbf{3.5.} See 0.1-0.7.

}

\bigskip

{\large{\sffamily\bfseries Chapter 4}}

{\small

\textbf{4.1.} A. F. Ioffe: Physics of Semiconductors, Infosearch, London (1960).

\textbf{4.2.} A. J. Dekker: Electrical Engineering Materials, Prentice-Hall, Englewood Cliffs, N. J. (1959).

\textbf{4.3.} G. A. Slack: ``Heat conduction in solids'' in Encyclopaedic Dictionary of Physics, J. Thewlis (Ed.) Vol. 3, Pergamon Press, Oxford (1961), 601-610.

\textbf{4.4.} See 0.1-0.8.

}

\bigskip

{\large{\sffamily\bfseries Chapter 5}}

{\small

\textbf{5.1.} J. Callaway: Energy Band Theory, Academic Press, New York (1964).

\textbf{5.2.} Semiconductors, N. B. Hannay (Ed.), Reinhold, New York (1959).

\textbf{5.3.} R. A. Smith: Semiconductors, Cambridge U.P., London (1959).

\textbf{5.4.} J. N. Shive: The Properties, Physics, and Design of Semiconductor Devices, Van Nostrand, Princeton, N.J. (1959).

\textbf{5.5.} See 0.1-0.9, 1.6, 3.3, 4.1.

}

\bigskip

{\large{\sffamily\bfseries Chapter 6}}

{\small

\textbf{6.1.} G. Mirdel: Elektrophysik, Berlin (1970).
\textbf{6.2.} A. C. Rose-Innes and E. H. Rhoderick: Introduction to Superconductivity, Pergamon Press, Oxford (1969).

\textbf{6.3.} J. Bardeen and J. R. Schrieffer: ``Recent developments in superconductivity'', in Progr. Low Temp. Phys., Vol. 3, Chapter 4, North-Holland, Amsterdam (1961).

\textbf{6.4.} D. H. Douglass and L. M. Falikov: ``The superconductivity energy gap'', in Progr. Low Temp. Phys., Vol. 4, Wiley, New York (1964), 97.

\textbf{6.5.} D. N. Langenberg, D. J. Scalapino, and B. N. Taylor: ``The Josephson effect'', Sci. Amer. 214, No. 5 (1966), 30-9.

\textbf{6.6.} J. Berdeen: Physics Today 26, No. 7 (1973).

\textbf{6.7.} J. Schrieffer: Physics Today 26, No. 7 (1973).

\textbf{6.8.} L. Cooper: Physics Today 26, No. 7 (1973).

\textbf{6.9.} J. Giaver: Science 183, No. 4131 (1974).

\textbf{6.10.} B. D. Josephson: Science 184, No. 4136 (1974).

\textbf{6.11.} W. P. Jolly: Cryoelectronics, The English U.P., London (1972).

\textbf{6.12.} See 0.1-0.9, 1.6, 2.1, 3.3, 4.1, 4.2, 5.2-5.4.

}

\bigskip

{\large{\sffamily\bfseries Chapter 7}}

{\small

\textbf{7.1.} S. V. Vonsovskii: The Contemporary Science of Magnetism, Gostekhizdat, Moscow-Leningrad (1953) (in Russian).

\textbf{7.2.} Ya. G. Dorfman: Magnetic Properties and Structure of Matter, Gostekhizdat, Moscow (1955) (in Russian).

\textbf{7.3.} L. V. Kirenskii: Magnetism, Izd-vo Akad. Nauk SSSR, Moscow (1963) (in Russian).

\textbf{7.4.} See 0.1-0.8, 1.6, 2.1, 3.3, 4.2.

}

\bigskip

{\large{\sffamily\bfseries Chapter 8}}

{\small

\textbf{8.1.} Ya. I. Fedotov: Fundamentals of Physics of Semiconductor Devices, ``Sovetskoe radio'', Moscow (1969) (in Russian).

\textbf{8.2.} I. P. Zherebtsov: Electronics (reprint of the 2nd edition), Mir Publishers, Moscow (1975).

\textbf{8.3.} V. V. Pasynkov, L. K. Chirkin, and A. D. Shinkov: Semiconductor Devices, ``Vysshaya shkola'', Moscow (1966) (in Russian).

\textbf{8.4.} A. F. Gorodetskii and A. F. Kravchenko: Semiconductor Devices, ``Vysshaya shkola'', Moscow (1967) (in Russian).

\textbf{8.5.} S. N. Levine: Principles of Solid-State Microelectronics, Holt, Rinehart and Winston, New York (1963).

\textbf{8.6.} J. H. Kalish: Microminiature Electronics, Bobbs-Merrill, Indianapolis (1967).

\textbf{8.7.} G. F. Alfrey: Physical Electronics, Van Nostrand, Princeton, N.J. (1964).

\textbf{8.8.} See 0.1-0.9, 1.6, 4.1, 5.2-5.4, 6.1.

}

\bigskip

{\large{\sffamily\bfseries Chapter 9}}

{\small

\textbf{9.1.} See 0.1-0.7, 0.9, 3.3, 4.1, 5.3, 5.4, 6.1.

}

%\pagestyle{mystyle}
